\meetingheader
    {Mar 09, 2026}
    {}
    {\meetinglinks{
        \meetinglink{Smelly Tool Descriptions (Feb 2026)}{https://arxiv.org/abs/2602.14878}
    }}
    {\begin{itemize}
        \item Fixed end-to-end pipeline: eval judge, training OOM, tool docstrings
        \item Validated local Qwen3.5-27B-FP8 as eval judge (replaces GPT-4 dependency)
        \item Agent successfully runs profile $\to$ filter $\to$ mix $\to$ train $\to$ eval loop
    \end{itemize}}
    {}


%% ============================================================
%% SECTION 1: PIPELINE FIXES
%% ============================================================

\section{Pipeline Fixes}

Three blockers prevented the agent from completing end-to-end episodes. All resolved this week.

\subsection{Eval judge: Qwen3.5-27B-FP8 replaces GPT-4}

VLMEvalKit requires an LLM judge for MMVet and MathVista\_MINI.
Previously required \texttt{OPENAI\_API\_KEY} $\to$ GPT-4o.
Now uses locally-served Qwen3.5-27B-FP8 via vLLM at \texttt{ARC\_API\_BASE}.

\begin{table}[H]
\centering
\small
\caption{Sanity check: LLaVA-1.5-7B zero-shot scores. Baseline column is a mix of paper-reported and VLMEvalKit-reproduced values; see Note column. Local Qwen3.5 judge within $\sim$1 point of baselines.}
\label{tab:judge-sanity}
\begin{tabular}{lccll}
\toprule
\textbf{Benchmark} & \textbf{Baseline} & \textbf{Ours (Qwen3.5 judge)} & \textbf{Source} & \textbf{Note} \\
\midrule
MMStar & 30.3 & 30.4 & \cite{chen2024mmstar} & from paper \\
OCRBench & 317 & 317 & \cite{liu2023ocrbench} & VLMEvalKit run (paper: 297) \\
HallusionBench & 27.6 & 27.6 & \cite{guan2024hallusionbench} & VLMEvalKit composite \\
MMMU\_DEV\_VAL & 35.3 & 35.3 & \cite{yue2024mmmu} & lmms-eval (val split) \\
MMVet & 31.1 & 30.2 & \cite{yu2024mmvet} & from paper \\
MathVista\_MINI & 26.1 & 25.4 & \cite{lu2024mathvista} & VLMEvalKit run \\
\bottomrule
\end{tabular}
\end{table}

\noindent Judge-dependent benchmarks (MMVet, MathVista) within 1 point --- acceptable for relative comparisons across curation runs.

\subsection{Training OOM: batch size fix}

LLaVA-1.5-7B full fine-tune on 2$\times$H200 (140GB each).
\texttt{per\_device\_train\_batch\_size=16} caused CUDA OOM at the cross-entropy loss.
Fixed to \texttt{batch\_size=2, grad\_accum=2} (effective batch 8).
Step time $\sim$2.8s/step, max 200 steps ($\sim$9.3 min).

\subsection{Tool docstrings: what + when format}

Rewrote all 13 tool docstrings following the ``smelly tool descriptions'' finding~\cite{smellyToolDesc2026}: only \textbf{what} (specific action) and \textbf{when} (usage context).
Removed verbose parameter explanations, examples, and caveats from the class-level docstring.

\subsection{Configurable training limits}

Moved hardcoded timeout and max\_steps to task YAML:
\begin{verbatim}
training_config:
  max_steps_cap: 200    # default 200
  timeout: 900          # default 900s
\end{verbatim}


%% ============================================================
%% SECTION 2: AGENT EPISODE OBSERVATIONS
%% ============================================================

\section{Agent Episode Observations}

With all fixes applied, the agent runs the full loop on 5 FineVision5 datasets (10k samples each, budget 10k).

\paragraph{Data ops are fast.}
Profiling, filtering, mixing, and saving complete in $<$1 min total.
\texttt{vlm\_filter} is the slowest data op ($\sim$5 min for image-heavy datasets due to full Arrow reload).
Training ($\sim$10 min) and eval ($\sim$5 min) dominate wall time as intended.

\paragraph{Agent self-corrects.}
When \texttt{quality\_filter} with strict thresholds dropped all rows (0/10k), the agent used \texttt{rollback} and retried with lenient parameters.

\paragraph{Captcha dataset always dropped.}
All images fail \texttt{vlm\_filter} (0/10k kept). The agent correctly excludes it from the mix.


%% ============================================================
%% KEY FINDINGS + TASKS
%% ============================================================

\keyfindings{
    \item \textbf{Local Qwen3.5-27B judge is viable.} Within 1 point of GPT-4o on all 6 benchmarks. Eliminates OpenAI dependency.
    \item \textbf{Training batch=2 is the max stable config for LLaVA on H200.} Batch=16 OOMs at cross-entropy; batch=2 with grad\_accum=2 gives effective batch 8.
    \item \textbf{Tool docstring format matters.} ``What + when'' only, per smelly tool descriptions paper. Removed verbose descriptions.
    \item \textbf{Data ops are not the bottleneck.} Sub-minute total. Train + eval dominate ($\sim$15 min/episode).
}

\meetingtasks{
    \item \todo{Validate full episode completes (train + eval) with batch=2 fix}
    \item \todo{Test multi-episode runs: does the agent improve curation strategy from eval feedback?}
    \item \todo{Explore agent architecture: split into specialized sub-agents (profiler, filterer, mixer) with phase-specific context}
    \item \todo{Measure token cost per episode and identify context window pressure points}
}
